Pre-processing high frequency animal tracking data

### 2020-09-14 02_filtering_data.Rmd
add new filtering code

# NB: set remove_inside to FALSE
data_inside_bbox <- atlastools::atl_filter_bounds(data = data,
                                                  x_range = c(0, 1),
                                                  y_range = c(0, 1),
                                                  remove_inside = FALSE)
```

```{r}
ggplot()+
  geom_path(data = data_copy, aes(x, y), col = "red")+
  geom_path(data = data_inside_bbox, aes(x, y))
```

@@

```{r example_remove_outliers, eval=FALSE}
# get speed and turning angle
data_many_nbs[, `:=`(in_speed = atl_get_speed(data_many_nbs,
                                              type = "in"),
                     out_speed = atl_get_speed(data_many_nbs,
                                               type = "out"),
                     angle = atl_turning_angle(data_many_nbs))]

@@

# filter the copy
data_non_move <- atl_filter_covariates(data_non_move,
                                       filters = c("in_speed < 0.001",
                                                   "out_speed < 0.001",
                                                   "angle < 40"))
```

@@

```{r}
sim_data <- mapply(function(p_outlier, ext_outlier, scale) {

@@

  land_props[, `:=`(scale = scale,
                    p_outlier = p_outlier,
                    ext_outlier = ext_outlier)]

  # make speed results
  speed_res <- data.table(type = c("reference", "outliers", "cleaned"),
                          speed_mean = unlist(lapply(list(speed, 
                                                          error_speed, 
                                                          clean_speed),
                                                     mean, na.rm = TRUE)),
                          speed_sd = unlist(lapply(list(speed, 
                                                          error_speed, 
                                                          clean_speed),
                                                     sd, na.rm = TRUE)),
                          scale = scale,
                          p_outlier = p_outlier,
                          ext_outlier = ext_outlier
                          )
  results <- list(land_props = land_props,
                  speed_res = speed_res)

  return(results)
}, 
param_c$p_outlier, 
param_c$ext_outlier,
param_c$land_scale,
SIMPLIFY = FALSE)
```

@@

# melt to
speed_data_long <- copy(speed_data)

speed_data_long <- melt(speed_data_long, 
                            id.vars = c("ext_outlier", "type",
                                        "p_outlier", "scale"))

ggplot(speed_data_long)+
  # geom_boxplot(aes(x = factor(land_values),
  #                  y = value,
  #                  group = interaction(variable, scale, land_values),
  #                  fill = variable))+
  geom_boxplot(aes(x = factor(ext_outlier),
                   y = value,
                   col = type))+
  facet_grid(~ variable, 
              scales = "free_y",
              labeller = label_both)+
  theme_classic()+
  theme(strip.background = element_rect(fill = "grey90",
                                        colour = NA))
```

>>>>

# NB: set remove_inside to FALSE
data_inside_bbox <- atlastools::atl_filter_bounds(data = data_copy,
                                                  x_range = c(0, 1),
                                                  y_range = c(0, 1),
                                                  remove_inside = FALSE)
```

```{r}
ggplot()+
  geom_path(data = data_copy, aes(x, y), col = "red")+
  geom_path(data = data_inside_bbox, aes(x, y))+
  theme_test()
```

@@

```{r example_remove_outliers, eval=FALSE}
# make a copy of the data
data_many_nbs <- copy(data_inside_bbox)

# get speed and turning angle
data_many_nbs[, `:=`(in_speed = atl_get_speed(data_many_nbs,
                                              type = "in"),
                     out_speed = atl_get_speed(data_many_nbs,
                                               type = "out"),
                     angle = atl_turning_angle(data_many_nbs))]

@@

# filter the copy
data_non_move <- atl_filter_covariates(data_non_move,
            filters = c("(in_speed < 0.001 & out_speed < 0.001) | angle < 40"))
```

@@

```{r}
sim_data <- mapply(function(p_outlier, ext_outlier, scale, replicate) {

@@

  land_props[, `:=`(scale = scale,
                    p_outlier = p_outlier,
                    ext_outlier = ext_outlier,
                    replicate = replicate)]

  # make speed results
  speed_res <- data.table(type = c("reference", "outliers", "cleaned"),
                          speed_mean = unlist(lapply(list(speed, 
                                                          error_speed, 
                                                          clean_speed),
                                                     mean, na.rm = TRUE)),
                          speed_sd = unlist(lapply(list(speed, 
                                                          error_speed, 
                                                          clean_speed),
                                                     sd, na.rm = TRUE)),
                          scale = scale,
                          p_outlier = p_outlier,
                          ext_outlier = ext_outlier,
                          replicate = replicate
                          )
  results <- list(land_props = land_props,
                  speed_res = speed_res)

  return(results)
}, 
param_c$p_outlier, 
param_c$ext_outlier,
param_c$land_scale,
param_c$replicate,
SIMPLIFY = FALSE)
```

@@

# cast wide
speed_data <- speed_data[, !"speed_sd"]

# find proportion of speed data
speed_data <- dcast(speed_data, 
      scale + p_outlier + ext_outlier + replicate ~ type, 
      value.var = "speed_mean")

# get proportion of speeds
speed_data[, `:=`(d_clean = cleaned * 100 / reference,
                  d_outlier = cleaned * 100 / reference)]

# melt
speed_data <- melt(speed_data[, !c("replicate", "cleaned", 
                                   "reference", "outliers")], 
                   id.vars = c("scale", "p_outlier", "ext_outlier"))

# summarise
speed_data <- speed_data[, list(mean = mean(value),
                                sd = sd(value)),
                         by = list(scale, p_outlier, ext_outlier, variable)]

ggplot(speed_data)+
  geom_pointrange(aes(factor(ext_outlier), mean - 100,
                      ymin = mean - sd - 100,
                      ymax = mean + sd - 100,
                      colour = scale,
                      group = interaction(scale, ext_outlier)),
                  position = position_dodge(width = 0.2))+
  geom_line(aes(factor(ext_outlier), mean - 100,
                      group = scale),
            position = position_dodge(width = 0.2))+
  theme_test()+
  theme(strip.background = element_rect(fill = "grey90",
                                        colour = NA))
```
